candidate genes

### 2019-12-15 analysis/10_specificgenes.Rmd
remove corrggplot thing

```{r setup, include=FALSE}
library(tidyverse)
library(cowplot)
library(corrr)
library(ggcorrplot)
library(pheatmap)

@@

corr <- x
row.names(corr) <- corr$rowname 
corr$rowname <- NULL
ggcorrplot(corr, hc.order = TRUE, outline.col = "white", title = "inc.d9 to inc.d17")
```

@@

corr <- x
row.names(corr) <- corr$rowname 
corr$rowname <- NULL
ggcorrplot(corr, hc.order = TRUE, outline.col = "white", title = "bldg to lay")
```

@@

corr <- x
row.names(corr) <- corr$rowname 
corr$rowname <- NULL
ggcorrplot(corr, hc.order = TRUE, outline.col = "white", title = "lay to inc.d3")
```

@@

corr <- x
row.names(corr) <- corr$rowname 
corr$rowname <- NULL
ggcorrplot(corr, hc.order = TRUE, outline.col = "white", title = "hatch to n5")
```

>>>>

```{r setup, include=FALSE}
library(tidyverse)
library(cowplot)
library(corrr)

@@

@@

@@

@@
